KeysarMouseTracking.csv

### 2017-07-20 analysis/cogSci_analysis.Rmd
Fix data paths; add new model vanity plot

criticalMessagesExp1 <- read.csv("../experiment1/data/message/analysis/messagesExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../analysis/messagesExp2.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

>>>>

criticalMessagesExp1 <- read.csv("./experiment1/data/processedLabelsExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../experiment2/data/processedLabelsExp2.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

```{r}
d.model <- data.frame(x = rep(c('red fish', 'blue fish'), 2),
                      y = c(0.27, 0.73, 0, 1),
                      source = c(rep('with speaker context-uncertainty', 2),
                                 rep('without speaker context-uncertainty', 2)))
ggplot(d.model, aes(x=x, y=y, fill = x)) +
  geom_bar(stat='identity', position = 'dodge') +
  theme_few() +
  scale_fill_manual(values = c('red', 'blue')) +
  facet_wrap(~ source) +
  ylab("")
```
